\label{page:pub}
\begin{center}
\textbf{\Large List of Publications}
\end{center}
\vspace*{25pt}
\begin{enumerate}[{[1]}]

\item S. Patil, A. Gupta, and M. Zaveri, ``Recovery of lost target in Wireless Sensor Network,'' \textit{submitted in EURASIP Journal on Wireless Communications and Networking}, (Revised Manuscript submitted).

\item S. Patil, A. Gupta, and M. Zaveri, ``Efficient target recovery in wireless sensor network,” \textit{in Advances in Computing and Information Technology}, ser. Advances in Intelligent Systems and Computing, Springer Berlin Heidelberg, 2012, vol. 176, pp. 385 – 394.

\item S. Patil, A. Gupta, and M. Zaveri, ``Localization in wireless sensor network: A distributed approach,” \textit{in Advances in Computing and Information Technology}, ser. Advances in Intelligent Systems and Computing, Springer Berlin Heidelberg, 2012, vol. 176, pp. 467-476.

\item A. Gupta, S. Patil, and M. Zaveri, ``Lost Target Recovery in Wireless Sensor Network Using Tracking,'' \textit{in proceedings of IEEE International Conference on Communication Systems and Network Technologies (CSNT)}. Rajkot,India: IEEE, May 2012, pp. 352–356.

\item S. Patil, and M. Zaveri, ``Localization in Wireless sensor Network with Nystrom Approximation,'' \textit{in International Journal of Wireless and Mobile Communication}, 3(5),Oct 2011, pp.37-48

\item S. Patil, and M. Zaveri, ``MDS and Trilateration based Localization in Wireless Sensor Network,'' \textit{in International Journal of Wireless Sensor Network, Scientific Research}, USA, 3(6), 2011, pp.198-208

\item S. Patil, and M. Zaveri, ``Energy efficient localization in Sensor network,'' \textit{in proceedings of IEEE International conference of HiPC 2011, (WonGen 2011)}, Banglore, 18-21 Dec. 2011

\item S. Patil, and M. Zaveri, ``Target Tracking approaches in Wireless sensor Network,'' \textit{in Proceedings of Computer Communication and Network, (CCN10)}, Florida, USA, 12-14 July 2010, pp.130-137

\end{enumerate}

\newpage